Predicting Tags for StackOverflow Posts

### 2013-06-28 stackExchange/writeups/iccm-2013/writeup.tex
foo
Former-commit-id: ee4819176add4ccd3ddba367011a2dc8567e00e7 [formerly 6b0abd22ed2424f49174b0c8f55dbe47e4bb4027]
Former-commit-id: 4f8bd67fa826263cc09ae517e085f99991bc3f9b
Final changes for ICCM paper
Former-commit-id: 7831a32e9283798e678b5be5cabb44feb122950e [formerly 15d5de80ad819e87f2b7d414475e8277b7662e51]
Former-commit-id: 9e646c1cc98b6d5e3f8f72cd60ff108b2245abf1

\begin{figure}[ht]
  \centering
  \resizebox{\linewidth}{!}{\includegraphics{visPost-2977094-act-crop.pdf}}
  \caption{
    Model's prediction of the top tags for post in Figure \ref{fig:examplePost}.
    At the top is the title text of the post, then the attentional weight (scaled entropy) for each word in the title, then the user-chosen tags.
    The bar graphs are the total activation for the top predicted model tags for the post.
    Each bar graph is partitioned into the three model components that vary across the tags in a single post.
}
  \label{fig:modelPost}
\end{figure}

@@

Our StackOverflow model is a successful case showing that ACT-R's declarative memory retrieval mechanisms scale, and can be applied to retrieval requests occurring across large-scale declarative memory datasets. 
The model can successfully tag 65\% of posts correctly, when tasked to predict one tag per post on average.
The model is also computationally space efficient:
Large-scale relational database techniques and efficient sparse matrix data structures were used for implementation,
so that the data structures require only 3GB of memory and retrieval requests with a DM dataset of \num{556677795} chunks occur in less than one second on a single processor.
Although certainly not perfect, model accuracy is significant and retrieval times are fast, so we are considering potential applications of the model in real-world settings.

@@

Alongside exploring the offset component and cognitive plausibility, our main planned research is to include the post author's past tagging behavior as an additional model predictor.
We are exploring a Bayesian updating technique that would adjust prior tag activations from global priors to user's priors as more tagging information about the user is collected.
For the StackOverflow dataset, adding user's tagging history to the model should improve predictive power for veteran users,
since programmers tend to specialize on a few set of tags that are of interest to them.

@@

We would like to thank Fred Oswald for his excellent guidance and feedback throughout the model development process.

>>>>

\begin{figure}[ht]
  \centering
  \resizebox{\linewidth}{!}{\includegraphics{visPost-2977094-act-crop.pdf}}
  \caption{
    Model's prediction of the top tags for post in Figure \ref{fig:examplePost}.
    At the top is the title text of the post, then the attentional weight (scaled entropy) for each word in the title, then the author-chosen tags.
    The bar graphs are the total activation for the top predicted model tags for the post.
    Each bar graph is partitioned into the three model components that vary across the tags in a single post.
}
  \label{fig:modelPost}
\end{figure}

@@

Our StackOverflow model is a successful case showing that ACT-R's declarative memory retrieval mechanisms scale, and can be applied to retrieval requests occurring across large-scale declarative memory datasets. 
The model can successfully tag 65\% of StackOverflow posts correctly, when tasked to predict one tag per post on average.
The model is also computationally space efficient:
Large-scale relational database techniques and efficient sparse matrix data structures were used for implementation,
so that the data structures require only 3GB of memory and retrieval requests with a DM dataset of \num{556677795} chunks occur in less than one second on a single processor.
Although certainly not perfect, model accuracy is significant and retrieval times are fast, so we are considering potential applications of the model in real-world settings.

@@

Alongside exploring the offset component and cognitive plausibility of the model, our main planned research is to include the post author's past tagging behavior as an additional model predictor.
We are exploring a Bayesian updating technique that would adjust prior tag activations from global priors to user's priors as more tagging information about the user is collected.
For the StackOverflow dataset, adding user's tagging history to the model should improve predictive power for veteran users,
since programmers tend to specialize on a few set of tags that are of interest to them.

@@

We would like to thank Fred Oswald for his excellent guidance and feedback throughout the model development and analysis process.
